Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-08 bbbq_article.tex
Mention NSA gap, fix #75

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores.png}
  \caption{
    Conservation scores across the SARS-CoV-2 proteome
    for proteins that have at least one TMH
  }
  \label{fig:evolutionary_conservation}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_all.png}
  \caption{
    Conservation scores across the SARS-CoV-2 proteome
    for all proteins
  }
  \label{fig:evolutionary_conservation}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_boxplot_all.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for all proteins
  }
  \label{fig:evolutionary_conservation_boxplot}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores.png}
  \caption{
    Evolutionary conservation
  }
  \label{fig:evolutionary_conservation_tmh}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_all.png}
  \caption{
    Evolutionary conservation
  }
  \label{fig:evolutionary_conservation_all}
\end{figure}

>>>>

Evolutionary conservation scores are shown in 
figures \ref{fig:evolutionary_conservation} (topology)
and \ref{fig:evolutionary_conservation_boxplot} (boxplot)
for proteins that have at least one TMH (see figures
\ref{fig:evolutionary_conservation_all} and 
\ref{fig:evolutionary_conservation_all_boxplot}
for the scores for all proteins).

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores.png}
  \caption{
    Conservation scores for the aligned SARS-CoV-2 proteomes,
    for proteins that have at least one TMH.
    The (non-logarithmic) scale of the conservation score has been removed
    for readability.
    Conservation scores do not start at residue 1 when
    an aligned protein sequence outflanks the consensus sequence 
    at the N-terminal
  }
  \label{fig:evolutionary_conservation}
\end{figure}

@@

@@

\begin{figure}[!htbp]
  \includegraphics[width=0.7\textwidth,scale=0.7]{bbbq_2/scores_all.png}
  \caption{
    Conservation scores for the aligned SARS-CoV-2 proteomes,
    for all proteins.
    The (non-logarithmic) scale of the conservation score has been removed
    for readability.
    Conservation scores do not start at residue 1 when
    an aligned protein sequence outflanks the consensus sequence 
    at the N-terminal.
  }
  \label{fig:evolutionary_conservation_all}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_boxplot_all.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for all proteins
  }
  \label{fig:evolutionary_conservation_all_boxplot}
\end{figure}
